Ensemble Stability of Biological Networks

### 2014-10-16 tex/figures.tex
update fig 1 legend

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.9\columnwidth]{fig/biomodelexamples.pdf}
\caption{{\bf Dynamical models in systems biology.} The top row represents a chemical reaction network (CRN) \cite{Shinar2010}, a gene regulatory network (GRN) \cite{Karlebach2008}, and an ecological regulatory network (ERN) \cite{Rohr2014} in terms of the graphical methods specific to each field mapped into the interaction graph, which provides a unified representation for networks across these fields. The third row represents a particular example of a system of differential equations that are used to model a biological network within each of the domains of application considered here \cite{Shinar2010,Karlebach2008,Shinar2010}. The fourth row shows the general form of a system of differential equations that can be used to model any network architecture of any size within each of the three domains of application exemplified here.}
\label{fig:biomodelexamples}
\end{figure}

>>>>

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.9\columnwidth]{fig/biomodelexamples.pdf}
\caption{{\bf Dynamical models in systems biology.} The top row represents a chemical reaction network (CRN) \cite{Shinar2010}, a gene regulatory network (GRN) \cite{Karlebach2008}, and an ecological regulatory network (ERN) \cite{Rohr2014} in terms of the graphical methods specific to each field mapped into the interaction graph, which provides a unified representation for networks across these fields. The second row represents a particular example of a system of differential equations that are used to model a biological network within each of the domains of application considered here \cite{Shinar2010,Karlebach2008,Shinar2010}. The third row shows the general form of a system of differential equations that can be used to model any network architecture of any size within each of the three domains of application exemplified here.}
\label{fig:biomodelexamples}
\end{figure}
